Appendix

### 2023-07-23 docs/index.qmd
Simplify dependencies

---
title: "Cognate beginnings to bilingual lexical acquisition"
subtitle: "Lab notes"
short-title: "Cognate beginnings"
author:
  - name: Gonzalo Garcia-Castro
    corresponding: true
    orcid: 0000-0002-8553-4209
    email: gonzalo.garciadecastro@upf.edu
    affiliations:
      - id: cbc
        name: Universitat Pompeu Fabra
        department: Center for Brain and Cognition
        address: Ramon Trias Fargas 25-27
        city: Barcelona
        region: Spain
        postal-code: "08005"
  - name: Daniela S. Avila-Varela
    orcid: 0000-0002-3518-8117
    affiliations: 
      - ref: cbc
      - id: ul
        name: Universidade de Lisboa
        department: Facultade de Letras
        address: Alameda da Universidade
        city: Lisboa
        region: Portugal
        postal-code: "1600-214"
  - name: Ignacio Castillejo
    orcid: 0000-0001-7445-0416
    affiliations: 
      - id: uam 
        name: Universidad Autónoma de Madrid
        department: Departamento de Psicología
        address: Iván Pavlov, 6
        city: Madrid
        region: Spain
        postal-code: "28049"
  - name: Nuria Sebastian-Galles
    orcid: 0000-0001-6938-2498
    affiliations: 
      - ref: cbc
date: "May 10th, 2023"
code-repo: "Access the code, data, and analysis at <https://github.com/gongcastro/trajectories>"
keywords:
  - lexical acquisition
  - vocabulary
  - bilingualism
  - item response theory
  - bayesian
csl: "../assets/apa7.csl"
bibliography: "../assets/references.bib"
link-citations: true
editor: source

code-fold: true
warning: false

format:
  html: default

fig-dpi: 1000
---

@@

yaml_metadata <- rmarkdown::yaml_front_matter(here::here("manuscript", "manuscript.qmd"))
title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
thanks <- yaml_metadata$thanks

```

>>>>

---
---

@@

yaml_metadata <- rmarkdown::yaml_front_matter(
    here::here("manuscript", "manuscript.qmd")
)

title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
thanks <- yaml_metadata$thanks
```

### 2023-07-23 manuscript/_appendix/_model-doe.qmd
Simplify dependencies

```{r tbl-coefs-doe}
#| label: tbl-coefs-doe
#| fig-cap: "Posterior distribution of regression coefficients of the model including the *Exposure* composite predictor, and of the model including lexical frequency (*Frequency*) and degree of exposure (*DoE*) separately. Median: median of the posterior distribution in the probability scale. 95\\% HDI: 95\\% highest density interval of the distribution. p(ROPE): overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero. In the right column, we show a graphical representation of the median and 95% HDI of each coefficient, with a reference dotted line indicating the location of zero."
#| echo: false
#| message: false
#| warning: false
# summarise posterior draws
tbl_data <- bind_rows("Exposure model" = model_summary,
                      "DoE-Frequency model" = posterior_doe_summary,
                      .id = ".model") |> 
    mutate(
        across(c(.median, .lower, .upper),
               function(x) {
                   ifelse(
                       .type=="Intercepts (at 22 months)",
                       plogis(x),
                       x/4
                   )
               }
        )) |>
    filter(.type == "Slopes") |> 
    select(.model, .variable_name, .median, .lower, .upper, .rope_overlap) |> 
    mutate(
        across(.median:.upper, plogis),
        .variable_name = gsub("×", '$\\\\times$', .variable_name),
        .hdi = paste0("[", round(.lower, 3),
                      ", ", round(.upper, 3), "]"),
        .rope_overlap = sub("^(-?)0.", "\\1.",
                            sprintf("%.3f", .rope_overlap))) |> 
    select(.variable_name, .median, .lower, .upper, .hdi, .rope_overlap)

>>>>

```{r tbl-coefs-doe}
#| label: tbl-coefs-doe
#| tbl-cap: "Posterior distribution of regression coefficients of the model including the *Exposure* composite predictor, and of the model including lexical frequency (*Frequency*) and degree of exposure (*DoE*) separately. Median: median of the posterior distribution in the probability scale. 95\\% HDI: 95\\% highest density interval of the distribution. *p*(ROPE): overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero. In the right column, we show a graphical representation of the median and 95% HDI of each coefficient, with a reference dotted line indicating the location of zero."
#| echo: false
#| message: false
#| warning: false
# summarise posterior draws
tbl_data <- list("Exposure model" = model_summary,
                 "DoE-Frequency model" = posterior_doe_summary) |> 
    purrr::map_df(\(x) mutate(x, across(.variable_name, as.character)),
                  .id = ".model") |> 
    mutate(
        across(c(.value, .lower, .upper),
               function(x) {
                   ifelse(
                       .type=="Intercepts (at 22 months)",
                       plogis(x),
                       x/4
                   )
               }
        )) |>
    filter(.type=="Slopes") |> 
    select(.model, .variable_name, .value, .lower, .upper, .rope) |> 
    mutate(
        across(.value:.upper, plogis),
        .variable_name = gsub("×", '$\\\\times$', .variable_name),
        .hdi = paste0("[", round(.lower, 3),
                      ", ", round(.upper, 3), "]"),
        .rope = sub("^(-?)0.", "\\1.",
                    sprintf("%.3f", .rope))) |> 
    select(.variable_name, .value, .lower, .upper, .hdi, .rope)

### 2023-07-23 manuscript/appendix.qmd
Simplify dependencies

---
csl: "../assets/apa7.csl"
bibliography: "../assets/references.bib"
link-citations: true
editor: source

@@

targets::tar_load(c(syllables_data, model_fit_syllables, post_syllables))

>>>>

---
csl: "_assets/apa7.csl"
bibliography: "_assets/references.bib"
link-citations: true
editor: source

@@

targets::tar_load(c(syllables_data, model_fit_syllables, post_syllables,
                    posterior_syllables_summary))
